---
title: "Data607_Assignment03"
author: "Ryan Weber"
date: "February 18, 2018"
output: 
  html_document:
    theme: lumen
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(stringr)
library(dplyr)
```

#### Raw string
```{r}
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
```


#### Extract names
```{r}
names <- unlist(str_extract_all(raw.data, "([[:alpha:]., ]){2,}"))
```

# 1. Output first and last name ordered

### Keep titles

#### If value contains ",", then switch the order of first and last
```{r}
ifelse(str_detect(names, ","), 
                str_c(str_extract(names, "[:word:]+$"), " ", str_extract(names,"^[:word:]+\\b")),
                names)
```


### Remove titles

#### Remove middle initials and/or Titles
```{r}
firstLast <- unlist(str_replace_all(names, "[:alpha:]+\\. ", ""))
firstLast
```

#### If value contains ",", then switch the order of first and last
```{r}
ifelse(str_detect(firstLast, ","), 
       str_c(str_extract(firstLast, "[:word:]+$"), " ", str_extract(firstLast,"^[:word:]+\\b")),
       firstLast)
```


# 2. Logical vector of names with a title
```{r}
str_detect(names, "^[:alpha:]+\\. ")
```


# 3. Logical vector or names with a "second name"
Assuming "second name" means middle name
```{r}
str_detect(names, "[^.] [:alpha:]+\\.? ")
```


# 4 Regex examples
#### a. [0-9]+\\$ 
What does it describe?  
 - Numbers followed by a dollar sign (prices in dollars?)
```{r}
str_detect("1234$", "[0-9]+\\$")
```
 
#### b. \\b[a-z]{1,4}\\b 
What does it describe?  
 - presence of a single, lowercase letter in a string or on a line
```{r}
str_detect(" a ", "\\b[a-z]\\b")
str_detect("z", "\\b[a-z]\\b")
```

#### c. .*?\\.txt$  
What does it describe?  
  - text file document name
```{r}
str_detect("temp.txt", ".*?\\.txt$")
str_detect("doc.temp.txt", ".*?\\.txt$")
```
  
#### d. \\d{2}/\\d{2}/\\d{4}
What does it describe?  
  - mdy or dmy dates
```{r}
str_detect("12/31/1980", "\\d{2}/\\d{2}/\\d{4}")
str_detect("31/12/1980", "\\d{2}/\\d{2}/\\d{4}")
```

#### e. <(.+?)>.+?</\\1> # Not clear to me what the first "?" adds, or the case where ".+?" is more restrictive than ".+"  
What does it describe?  
  - whole xml tag sequence with sometime in between
```{r}
  unlist(str_extract_all("<html><abc></abc></html>", "<(.+?)>.+?</\\1>"))
  unlist(str_extract_all("<html><abc>asdf</abc></html>", "<(.+?)>.+?</\\1>"))
  unlist(str_extract_all("<html> </html>", "<(.+?)>.+?</\\1>"))
  unlist(str_extract_all("<html> </html>", "<(.+?)>.*</\\1>"))
  unlist(str_extract_all("<html><script>asdf</script><body><text>def</text></body></html>", "<(.+)>.+</\\1>"))
```

9.  Try to decode string

#### String to decode
```{r}
code <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
```

#### Inspect
```{r}
nums <- unlist(str_extract_all(code, "[:digit:]+|[:punct:]+"))
nums

letters <- unlist(str_extract_all(code, "[:alpha:]+"))
letters
```

#### Do numbers point to letters in the string?
#### 905 much larger than string length
```{r}
str_length(str_c(letters, collapse=""))
```


#### See what capital letters there are
```{r}
capLetters <- str_extract_all(code, "[A-Z]")
capLetters
```

oh

LKJLgKASJDeFOIJOOIeJGNOIAJtSDOFhINUAOaPSFInUOkDsJ!